### 2020-04-08 thesis/content/chapter-evaluation.tex
started with real-world eval section + various improvements

In our experimental evaluation we focus on two types of learners:
\acp{svm} using graph kernels and \acp{gcnn}.
We evaluate those learners by comparing their test accuracies on multiple binary classification problems.
To obtain those accuracies we follow the graph classification benchmarking framework recently proposed by \citet{Errica2020}.
Their benchmarking framework is motivated by the observation that most recent publications in the field of \acp{gnn} do not provide reproducible results.
To tackle this issue they evaluated multiple state-of-the-art methods using a unified model selection procedure:\\
{\setlength{\intextsep}{0pt}
\begin{minipage}[t]{0.55\linewidth-1em}
	\begin{algorithm}[H]
		\caption{$k$-fold Model Assessment}\label{algo:eval:assessment}
		\begin{algorithmic}[1]
			\State{\textbf{Input:} Dataset $\mathcal{D}$, configurations $\Theta$}
			\State{Split $\mathcal{D}$ into $k$ folds $F_1, \dots, F_{k}$}
			\For{$i \leftarrow 1, \dots, k$}
				\State{$\mathcal{D}_{\mathrm{train/val}}, \mathcal{D}_{\mathrm{test}} \leftarrow \left( \bigcup_{j \neq i} F_{j} \right), F_i$}
				\State{Split $\mathcal{D}_{\mathrm{train/val}}$ into $\mathcal{D}_{\mathrm{train}}, \mathcal{D}_{\mathrm{val}}$}
				\State{$\theta_{\mathrm{best}} \leftarrow \Call{Select}{\mathcal{D}_{\mathrm{train}}, \mathcal{D}_{\mathrm{val}}, \Theta}$}
				\For{$r \leftarrow 1, \dots, R$}
					\State{$h_{i,r} \leftarrow \Call{Train}{\mathcal{D}_{\mathrm{train}}, \theta_{\mathrm{best}}}$}
					\State{$\mathit{acc}_{i,r} \leftarrow \Call{Eval}{h_{i,r}, \mathcal{D}_{\mathrm{test}}}$}
				\EndFor{}
				\State{$\mathit{acc}_{i} \leftarrow \mean_{r \in [R]}{\mathit{acc}_{i,r}}$}
			\EndFor{}
			\State{\Return{$\mean_{i \in [k]} \mathit{acc}_i, \mathrm{stddev}_{i \in [k]}\, \mathit{acc}_i$}}
		\end{algorithmic}
	\end{algorithm}
\end{minipage}\hspace*{1em}%
\begin{minipage}[t]{0.45\linewidth}
	\begin{algorithm}[H]
		\caption{Model Selection}\label{algo:eval:selection}
		\begin{algorithmic}[1]
			\Function{Select}{$\mathcal{D}_{\mathrm{train}}, \mathcal{D}_{\mathrm{val}}, \Theta$}
			\ForAll{$\theta \in \Theta$}
				\State{$h_{\theta} \leftarrow \Call{Train}{\mathcal{D}_{\mathrm{train}}, \theta}$}
				\State{$\mathit{acc}_{\theta} \leftarrow \Call{Eval}{h_{\theta}, \mathcal{D}_{\mathrm{val}}}$}
			\EndFor{}
			\State{$\theta_{\mathrm{best}} \leftarrow \arg\max_{\theta \in \Theta}{\mathit{acc}_{\theta}}$}
			\State{\Return{$\theta_{\mathrm{best}}$}}
			\EndFunction{}
		\end{algorithmic}
	\end{algorithm}
\end{minipage}}

We base our evaluations on this assessment strategy with $k = 10$ folds and $r = 3$ repeats per fold to smooth out differences caused by random weight initializations.
For each dataset the same folds are used across the evaluated models; class proportions are preserved within each fold by using stratified splits.
To keep the total runtime of the experiments feasible, a single 90\%/10\% holdout split into training and validation data is used instead of cross-validation.
In each experiment, training is performed with an early stopping condition which cancels the optimization if there is no improvement to the validation loss for more than $p$ epochs.
The patience period $p$ is part of the hyperparameter configurations $\theta \in \Theta$.

Using this assessment strategy we evaluate \acp{svm} with the following graph kernels:
\begin{enumerate}[label={\textbf{\arabic*.}},itemsep=2pt,parsep=2pt]
	\item \textbf{\ac{wl} subtree kernel (\acs{wl}\textsubscript{ST})} with the iteration counts $T \in [5]$ to evaluate the influence of the depth of \ac{bfs} subtrees which span \ac{lta} constituents.
	\item \textbf{\ac{wl} shortest path kernel (\acs{wl}\textsubscript{SP})} with the iteration count $T = 5$.
	\item \textbf{2-LWL kernel} with the iteration count $T = 3$.
	\item \textbf{2-GWL kernel} with the iteration count $T = 3$.
\end{enumerate}
The gram matrices of the \acs{wl}\textsubscript{ST} and \acs{wl}\textsubscript{SP} kernels are computed via the \citetitle{GK} library~\cite{Siglidis2018}\cite{GK}.
For the gram matrices of the two dimensional \ac{wl} kernels we use a modified version\footnote{\url{https://github.com/Cortys/glocalwl}} of the reference implementation provided by \citet{Morris2017}.
To train \acp{svm} with those kernels, \citetitle{SKL}~\cite{Pedregosa2011}\cite{SKL} is used.
For the evaluation of \acp{gcnn} we selected the following methods:
\begin{enumerate}[label={\textbf{\arabic*.}},itemsep=2pt,parsep=2pt]
	\item \textbf{Structure unaware baseline:}
		\citet{Errica2020} describe a simple model which simply applies a standard \ac{mlp} to each individual vertex feature vector, then sums up the resulting feature vectors and applies another \ac{mlp} to the vector sum.
		This approach does not use any structural information and therefore serves as a baseline to detect whether a \ac{gnn} is able to exploit graph structure.
	\item \textbf{\ac{gin}} is evaluated as described by \citet{Xu2018}, i.e.\ with a sum pooling layer and an appended \ac{mlp} to produce the final prediction.
	\item \textbf{2-\acs{gnn}} is evaluated with both a static $\mean$ pooling layer and with \ac{sampool} (see \cfullref{defn:ltag:sam-pool}).
		After the pooling layer a \ac{mlp} is used to produce the final prediction.
	\item \textbf{2-\acs{wl}-\ac{gnn}} \textit{(our method)} is evaluated using the same configurations as 2-\acs{gnn}.
		To test the \ac{lta} assumption we additionally evaluate it in \acs{lta}-like configurations, i.e.\ with a stack of 2-\acs{wl} convolutions that produce a local prediction $y_{ij} \in [0, 1]$ for each edge $e_{ij}$ and without the final \ac{mlp}.
\end{enumerate}
The baseline and \ac{gin} results are obtained using the PyTorch-based implementation provided by \citet{Errica2020}.
For both 2-\acs{gnn} and 2-\acs{wl}-\ac{gnn} a custom TensorFlow-based implementation is used.
The code for all conducted experiments as well as the used dataset splits are available GitHub\footnote{\url{https://github.com/Cortys/master-thesis}}.

@@

Based on this problem we generated a synthetic triangle detection dataset.
It contains randomly generated graphs with varying vertex counts and vertex color proportions (see \cref{sec:appendix:ds-stats} for a more detailed description).
We use this dataset to evaluate whether a learner is able to ignore varying amounts of noisy random structure and focus on relevant local substructures, in this case unicolored triangles.
\begin{table}[t]
	\caption{Mean accuracies and standard deviations on the triangle detection dataset.}\label{tbl:eval:synthetic}
	\centering
	\csvreader[
		tabular={clrrr},
		separator=semicolon,
		table head={%
			& \multicolumn{2}{l}{Model (Iterations/Pooling)} & \multicolumn{1}{c}{Train} & \multicolumn{1}{c}{Test} \\\toprule%
		},
		table foot=\bottomrule,
		late after line=\ifthenelse{\equal{\id}{9}}{\\\midrule}{\\},
		head to column names,
		filter=\equal{\isDefault}{1}\or\equal{\id}{0}
	]{data/results.csv}{}{%
		\ifthenelse{\equal{\id}{0}}{\multirow{5}{*}[0em]{\rotatebox[origin=c]{90}{\small\textsc{Kernel}}}}{}%
		\ifthenelse{\equal{\id}{9}}{\multirow{8}{*}[0em]{\rotatebox[origin=c]{90}{\small\textsc{\ac{gnn}}}}}{} &%
		\textbf{\model} ($\params$) & \ifthenelse{\equal{\isLta}{1}}{\badgeboxinline[t_green]{\scriptsize \acs*{lta}-like}}{} &%
		$\condbold{\triangleBestTrain}{\triangleTrainMean} \pm \triangleTrainStd$ & $\condbold{\triangleBestTest}{\triangleTestMean} \pm \triangleTestStd$%
	}
\end{table}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\linewidth]{gfx/evaluation/triangle-problem.pdf}
	\caption[Two example graphs from the triangle detection dataset.]{
		Two examples from the triangle detection dataset.
		The unique unicolored triangle which has to be detected by the learners is highlighted in both graphs.
	}\label{fig:evaluation:triangle-problem}
\end{figure}
Looking at the results in \cref{tbl:eval:synthetic}, it can be seen that the structure unaware baseline method is completely unable to do so, as expected.
The structure aware learners on the other hand all perform better than random guessing and are in fact mostly able to fit the training data perfectly.
This shows that all generated graphs are 1-\acs{wl} distinguishable; the \ac{wl} subtree kernel for example can simply memorize the training graphs via their unique 1-\acs{wl} color distribution after $T = 5$ refinement steps.

@@

Looking at the 2-\acs{wl} inspired \acp{gnn} (2-\acs{gnn}, 2-\acs{wl}-\acs{gnn}), we find that the proposed 2-\acs{wl}-\acs{gnn} significantly outperforms all other evaluated methods which confirms our theoretical results from \cref{sec:ltd:wl2gnn:properties}.
We evaluated 2-\acs{wl}-\acsp{gnn} in an \acs{lta}-like configuration without a final \ac{mlp} and in a non-\acs{lta} configuration with an \ac{mlp} after the pooling layer.
Comparing both configurations we clearly see that the \acs{lta}-variant has a worse generalization performance despite the fact that the triangle detection problem fits well into the \ac{lta} framework:
Find the unicolored triangle constituent, classify it locally then use that local class to classify the graph.
Further investigations are required to determine to which extent the worse performance of the \acs{lta}-like configuration is caused by the static subtree-based constituents and whether a more dynamic solution to the \acf{ltd} problem could improve the performance (e.g.\ via the edge filters described in \cref{sec:ltd:edge-filter}).

Finally, looking at the two evaluated \acs{lta}-compatible pooling layers, static $\mean$ pooling and \ac{sampool}, we see that the attention mechanism significantly improves the generalization performance of both 2-\acs{gnn} and 2-\acs{wl}-\acs{gnn}.
This indicates that \ac{sampool} is successful at filtering out the randomly generated noisy parts of a given graph and put most attention to the relevant unicolored triangle.

@@

>>>>

In our experimental evaluation we focus on two types of learners:
\acp{svm} using graph kernels and \acp{gcnn}.
We evaluate those learners by comparing their test accuracies on multiple binary classification problems.
To obtain those accuracies we follow the graph classification benchmarking framework recently proposed by \citet{Errica2020}.
Their benchmarking framework is motivated by the observation that most recent publications in the field of \acp{gnn} do not provide reproducible results.
To tackle this issue they evaluated multiple state-of-the-art methods using a unified model selection procedure:\\
{\setlength{\intextsep}{0pt}%
\begin{minipage}[t]{0.55\linewidth-1em}
	\begin{algorithm}[H]
		\caption{$k$-fold Model Assessment}\label{algo:eval:assessment}
		\begin{algorithmic}[1]
			\State{\textbf{Input:} Dataset $\mathcal{D}$, configurations $\Theta$}
			\State{Split $\mathcal{D}$ into $k$ folds $F_1, \dots, F_{k}$}
			\For{$i \leftarrow 1, \dots, k$}
				\State{$\mathcal{D}_{\mathrm{train/val}}, \mathcal{D}_{\mathrm{test}} \leftarrow \left( \bigcup_{j \neq i} F_{j} \right), F_i$}
				\State{Split $\mathcal{D}_{\mathrm{train/val}}$ into $\mathcal{D}_{\mathrm{train}}, \mathcal{D}_{\mathrm{val}}$}
				\State{$\theta_{\mathrm{best}} \leftarrow \Call{Select}{\mathcal{D}_{\mathrm{train}}, \mathcal{D}_{\mathrm{val}}, \Theta}$}
				\For{$r \leftarrow 1, \dots, R$}
					\State{$h_{i,r} \leftarrow \Call{Train}{\mathcal{D}_{\mathrm{train}}, \theta_{\mathrm{best}}}$}
					\State{$\mathit{acc}_{i,r} \leftarrow \Call{Eval}{h_{i,r}, \mathcal{D}_{\mathrm{test}}}$}
				\EndFor{}
				\State{$\mathit{acc}_{i} \leftarrow \mean_{r \in [R]}{\mathit{acc}_{i,r}}$}
			\EndFor{}
			\State{\Return{$\mean_{i \in [k]} \mathit{acc}_i, \mathrm{stddev}_{i \in [k]}\, \mathit{acc}_i$}}
		\end{algorithmic}
	\end{algorithm}
\end{minipage}\hspace*{1em}%
\begin{minipage}[t]{0.45\linewidth}
	\begin{algorithm}[H]
		\caption{Model Selection}\label{algo:eval:selection}
		\begin{algorithmic}[1]
			\Function{Select}{$\mathcal{D}_{\mathrm{train}}, \mathcal{D}_{\mathrm{val}}, \Theta$}
			\ForAll{$\theta \in \Theta$}
				\State{$h_{\theta} \leftarrow \Call{Train}{\mathcal{D}_{\mathrm{train}}, \theta}$}
				\State{$\mathit{acc}_{\theta} \leftarrow \Call{Eval}{h_{\theta}, \mathcal{D}_{\mathrm{val}}}$}
			\EndFor{}
			\State{$\theta_{\mathrm{best}} \leftarrow \arg\max_{\theta \in \Theta}{\mathit{acc}_{\theta}}$}
			\State{\Return{$\theta_{\mathrm{best}}$}}
			\EndFunction{}
		\end{algorithmic}
	\end{algorithm}
\end{minipage}}

We base our evaluations on this assessment strategy with $k = 10$ folds and $r = 3$ repeats per fold to smooth out differences caused by random weight initializations.
For each dataset the same folds are used across the evaluated models; class proportions are preserved within each fold by using stratified splits.
To keep the total runtime of the experiments feasible, a single 90\%/10\% holdout split into training and validation data is used instead of cross-validation.
To train models that require gradient-based optimization, we use the well-known Adam optimizer~\cite{Kingma2015}.
In all experiments, training is performed with an early stopping condition which cancels the optimization if there is no improvement to the validation loss for more than $p$ epochs.
The patience period $p$ is part of the hyperparameter configurations $\theta \in \Theta$.

Using this assessment strategy we evaluate \acp{svm} with the following graph kernels:
\begin{enumerate}[label={\textbf{\arabic*.}},itemsep=2pt,parsep=2pt]
	\item \textbf{\ac{wl} subtree kernel (\acs{wl}\textsubscript{ST})} with the iteration counts $T \in [5]$ to evaluate the influence of the depth of \ac{bfs} subtrees which span \ac{lta} constituents.
	\item \textbf{\ac{wl} shortest path kernel (\acs{wl}\textsubscript{SP})} with the iteration count $T = 5$.
	\item \textbf{2-LWL kernel} with the iteration count $T = 3$.
	\item \textbf{2-GWL kernel} with the iteration count $T = 3$.
\end{enumerate}
The gram matrices of the \acs{wl}\textsubscript{ST} and \acs{wl}\textsubscript{SP} kernels are computed via the \citetitle{GK} library~\cite{Siglidis2018}\cite{GK}.
For the gram matrices of the two dimensional \ac{wl} kernels we use a modified version\footnote{\url{https://github.com/Cortys/glocalwl}} of the reference implementation provided by \citet{Morris2017}.
To train \acp{svm} with those kernels, \citetitle{SKL}~\cite{Pedregosa2011}\cite{SKL} is used.
For the evaluation of \acp{gcnn} we selected the following methods:
\begin{enumerate}[label={\textbf{\arabic*.}},itemsep=2pt,parsep=2pt]
	\item \textbf{Structure unaware baseline:}
		\citet{Errica2020} describe a simple model which simply applies a standard \ac{mlp} to each individual vertex feature vector, then sums up the resulting feature vectors and applies another \ac{mlp} to the vector sum.
		This approach does not use any structural information and therefore serves as a baseline to detect whether a \ac{gnn} is able to exploit graph structure.
	\item \textbf{\ac{gin}} is evaluated as described by \citet{Xu2018}, i.e.\ with a sum pooling layer and an appended \ac{mlp} to produce the final prediction.
	\item \textbf{2-\acs{gnn}} is evaluated with both a static $\mean$ pooling layer and with \ac{sampool} (see \cfullref{defn:ltag:sam-pool}).
		After the pooling layer a \ac{mlp} is used to produce the final prediction.
	\item \textbf{2-\acs{wl}-\ac{gnn}} \textit{(our method)} is also evaluated with $\mean$ pooling and \ac{sampool}, just like 2-\ac{gnn}.
		To test the \ac{lta} assumption we evaluate 2-\acs{wl}-\acs{gnn} in an \acs{lta}-like configuration and in a non-\acs{lta} configuration.
		The \acs{lta}-like configuration uses a stack of 2-\acs{wl} convolutions that produce a local prediction $y_{ij} \in [0, 1]$ for each edge $e_{ij}$ instead of a local feature vector $z_{ij} \in \mathbb{R}^{d^{(T)}}$ and it does not have an \ac{mlp} after the pooling/aggregation layer.
\end{enumerate}
The baseline and \ac{gin} results are obtained using the PyTorch-based implementation provided by \citet{Errica2020}.
For both 2-\acs{gnn} and 2-\acs{wl}-\ac{gnn} a custom TensorFlow-based implementation is used.
The code for all conducted experiments as well as the used dataset splits are available GitHub\footnote{\url{https://github.com/Cortys/master-thesis}}.

@@

Based on this problem we generated a synthetic triangle detection dataset.
It contains randomly generated graphs with varying vertex counts and vertex color proportions (see \cref{sec:appendix:ds-stats} for a more detailed description).
We use this dataset to evaluate whether a learner is able to ignore varying amounts of noisy random structure and focus on relevant local substructures, in this case unicolored triangles.
\begin{table}[t]
	\caption{Mean accuracies and standard deviations on the triangle detection dataset.}\label{tbl:eval:synthetic}
	\centering
	\csvreader[
		tabular={clrrr},
		separator=semicolon,
		table head={%
			& \multicolumn{2}{l}{Model (Iterations/Pooling)} & \multicolumn{1}{c}{Train} & \multicolumn{1}{c}{Test} \\\toprule%
		},
		table foot=\bottomrule,
		late after line=\ifthenelse{\equal{\id}{9}}{\\\midrule}{\\},
		head to column names,
		filter=\equal{\isDefault}{1}
	]{data/results.csv}{}{%
		\ifthenelse{\equal{\id}{0}}{\multirow{5}{*}[0em]{\rotatebox[origin=c]{90}{\small\textsc{Kernel}}}}{}%
		\ifthenelse{\equal{\id}{9}}{\multirow{8}{*}[0em]{\rotatebox[origin=c]{90}{\small\textsc{\ac{gnn}}}}}{} &%
		\textbf{\ifthenelse{\equal{\isLta}{1}}{\textcolor{t_darkgreen}{\model*}}{\model\ifthenelse{\equal{\model}{2-WL-GNN}}{\phantom{*}}{}}} ($\params$) & \ifthenelse{\equal{\isLta}{1}}{\badgeboxinline[t_green]{\scriptsize \acs*{lta}-like}}{} &%
		\evalres{\triangleBestTrain}{\triangleTrainMean}{\triangleTrainStd} & \evalres{\triangleBestTest}{\triangleTestMean}{\triangleTestStd}%
	}
\end{table}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\linewidth]{gfx/evaluation/triangle-problem.pdf}
	\caption[Two example graphs from the triangle detection dataset.]{
		Two examples from the triangle detection dataset.
		The unique unicolored triangle which has to be detected by the learners is highlighted in both graphs.
	}\label{fig:evaluation:triangle-problem}
\end{figure}
Looking at the results in \cref{tbl:eval:synthetic}, it can be seen that the structure unaware baseline method is completely unable to do so, as expected.
The structure aware learners on the other hand all perform better than random guessing and are in fact mostly able to fit the training data perfectly.
This shows that all generated graphs are 1-\acs{wl} distinguishable; the \ac{wl} subtree kernel for example can simply memorize the training graphs via their unique 1-\acs{wl} color distribution after $T = 5$ refinement steps.

@@

Looking at the 2-\acs{wl} inspired \acp{gnn} (2-\acs{gnn}, 2-\acs{wl}-\acs{gnn}), we find that the proposed 2-\acs{wl}-\acs{gnn} significantly outperforms all other evaluated methods which confirms our theoretical results from \cref{sec:ltd:wl2gnn:properties}.
We evaluated 2-\acs{wl}-\acsp{gnn} in an \acs{lta}-like configuration without a final \ac{mlp} and in a non-\acs{lta} configuration with an \ac{mlp} after the pooling layer.
Comparing both configurations, we see that the \acs{lta}-variant has a worse generalization performance despite the fact that the triangle detection problem fits well into the \ac{lta} framework:
\begin{enumerate*}[label={\circled{\small\arabic*}}]
	\item Decomposition corresponds to finding a single unicolored triangle constituent,
	\item local evaluation then corresponds to checking the color of the triangle constituent and
	\item aggregation is trivial since there is only one constituent.
\end{enumerate*}

However, as we saw in the \ac{lta} formulation of \acp{gcnn} (see \cfullref{thm:ltag:gcnn-ltag-formulation}), a 2-\acs{wl}-\acs{gnn} does not actually learn to decompose a graph into unicolored triangle constituents but uses subtree constituents instead.
Further investigations are required to determine to which extent the worse performance of the \acs{lta}-like configuration is caused by this static decomposition strategy and whether a more dynamic solution to the \acf{ltd} problem could improve the performance (e.g.\ via the edge filtering idea described in \cref{sec:ltd:edge-filter}).

Finally, if we look at the two evaluated pooling layers, static $\mean$ pooling and \ac{sampool}, we see that the attention mechanism of the latter significantly improves the generalization performance of both 2-\acs{gnn} and 2-\acs{wl}-\acs{gnn}.
This indicates that \ac{sampool} is successful at filtering out the randomly generated noisy parts of a given graph and putting most attention to the relevant unicolored triangle.

@@

Since the synthetic triangle detection problem was designed specifically to highlight the advantages of a higher dimensional \ac{wl} method such as 2-\ac{wl}-\acsp{gnn}, we now evaluate the approaches more fairly on five common graph classification benchmark datasets from three different real-world domains.

\begin{table}[ht]
	\caption[Mean test accuracies and standard deviations on real-world data.]{
		Mean test accuracies and standard deviations on real-world data.
		\hfill\textcolor{t_darkgreen}{*}\,\badgeboxinline[t_green]{\scriptsize\acs*{lta}-like}
	}\label{tbl:eval:real}
	\centering
	\csvreader[
		tabular={lrrrrr},
		separator=semicolon,
		table head={%
			& %
			\multicolumn{1}{c}{\textbf{NCI1}} &%
			\multicolumn{1}{c}{\textbf{PROTEINS}} &%
			\multicolumn{1}{c}{\textbf{D\&D}} &%
			\multicolumn{1}{c}{\textbf{REDDIT}} &%
			\multicolumn{1}{c}{\textbf{IMDB}}%
			\\\toprule%
		},
		table foot=\bottomrule,
		late after line=\ifthenelse{\equal{\id}{9}}{\\\midrule}{\\},
		head to column names,
		filter={\equal{\isDefault}{1}}
	]{data/results.csv}{}{%
		% \ifthenelse{\equal{\id}{0}}{\multirow{5}{*}[0em]{\rotatebox[origin=c]{90}{\small\textsc{Kernel}}}}{}%
		% \ifthenelse{\equal{\id}{9}}{\multirow{8}{*}[0em]{\rotatebox[origin=c]{90}{\small\textsc{\ac{gnn}}}}}{} &%
		\textbf{\ifthenelse{\equal{\isLta}{1}}{\textcolor{t_darkgreen}{\model*}}{\model\ifthenelse{\equal{\model}{2-WL-GNN}}{\phantom{*}}{}}} {\footnotesize($\params$)} &%
		{\small\evalres{\nciBestTest}{\nciTestMean}{\nciTestStd}}&%
		{\small\evalres{\proteinsBestTest}{\proteinsTestMean}{\proteinsTestStd}}&%
		{\small\evalres{\ddBestTest}{\ddTestMean}{\ddTestStd}}&%
		{\small\evalres{\redditBestTest}{\redditTestMean}{\redditTestStd}}&%
		{\small\evalres{\imdbBestTest}{\imdbTestMean}{\imdbTestStd}}%
	}
\end{table}
